iterSim

### 2023-12-17 analyses/optimFlchain.Rmd
Improved documentation for potential users

```{r}
library(reticulate)

@@

##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)

#baselineTrials<-2

reoptimize=T

finalFit=T
```

#5 fold cross validation to select best hyperparameters, average performance on a test set.

```{r flchainPrep,eval=TRUE,hide=FALSE}

library(survival)
flchain<-flchain

preData<-data.frame(age=as.numeric(flchain$age),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

modData<-as.data.frame(model.matrix(~.,preData)[,-1])

data<-as.data.frame(apply(modData,2,as.numeric))

spec = c(train = .85, test = .15)

g = sample(cut(
  seq(nrow(data)), 
  nrow(data)*cumsum(c(0,spec)),
  labels = names(spec)
))

res = split(data, g)

@@

k=3
klist<-list()
data<-res$train
for(i in 1:k){

  spec = c(train = .85, val = .15)

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/flchainCV.rds")

@@

```{r setFixedHyperparameters,eval=TRUE,hide=FALSE}

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/flchainCV.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/flchainCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/flchainCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r winners,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

@@

winners<-readRDS("cvData/flchainWins.rds")

klist<-readRDS("cvData/flchainCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
AUClist<-list()
pos<-1

spec = c(train = .85, validate = .15)

g = sample(cut(
  seq(nrow(data)), 
  nrow(data)*cumsum(c(0,spec)),
  labels = names(spec)
))

res = split(data, g)

@@

  trainOG<-res$train

  numSamp<-nrow(trainOG)
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]

  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)

  fullTest<-readRDS("cvData/flchainTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

  val<-normalizer(res$validate,means,sds,maxTime)

  train<-normalizer(train,means,sds,maxTime)

  linModelTrain<-as.data.frame(rbind(train,val))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

  times<-head(times, -1)
  times<-tail(times, -1)

@@

@@

```{r auc}

AUClist<-readRDS('results/100flchainAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

>>>>

```{r}
# First load reticulate , then initialize python environment for CUDA (I turn it off as we only had one gpu and the 4 analyses were run in parallel)
library(reticulate)

@@

##########################
###Shared Hyperparameters
##########################
min_delta = 0
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
reoptimize=T
finalFit=T
```

# 3 fold cross validation to select best hyperparameters, average performance on a test set.

```{r flchainPrep,eval=TRUE,hide=FALSE}
##############################
### Process data to prepare for analysis
##############################
library(survival)
flchain<-flchain
preData<-data.frame(age=as.numeric(flchain$age),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

modData<-as.data.frame(model.matrix(~.,preData)[,-1])
data<-as.data.frame(apply(modData,2,as.numeric))
spec = c(train = .85, test = .15)
g = sample(cut(
  seq(nrow(data)), 
  nrow(data)*cumsum(c(0,spec)),
  labels = names(spec)
))
res = split(data, g)

@@

k=3
klist<-list()
data<-res$train
for(i in 1:k){
  spec = c(train = .85, val = .15)
  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/flchainCV.rds")

@@

```{r setFixedHyperparameters,eval=TRUE,hide=FALSE}
##################################
###Set up hyperparameter search space
##################################

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}

###############################
### optimize hyperparameters for DeepSurv
###############################
klist<-readRDS("cvData/flchainCV.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}

###############################
### optimize hyperparameters for DeepHit
###############################
klist<-readRDS("cvData/flchainCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}

###############################
### optimize hyperparameters for CBNN
###############################
klist<-readRDS("cvData/flchainCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r winners,eval=TRUE,hide=FALSE}

###############################
### save the best performaning hyperparameter sets
###############################
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

@@

#####################################
### run 100 fold bootstrap on the training set for each method
#####################################

#prepare data
winners<-readRDS("cvData/flchainWins.rds")
klist<-readRDS("cvData/flchainCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

#initialize data
start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
AUClist<-list()
pos<-1

# split training validation sets
spec = c(train = .85, validate = .15)
g = sample(cut(
  seq(nrow(data)), 
  nrow(data)*cumsum(c(0,spec)),
  labels = names(spec)
))
res = split(data, g)

@@

  #prepare data
  trainOG<-res$train
  numSamp<-nrow(trainOG)
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  val<-res$validate
  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)
  fullTest<-readRDS("cvData/flchainTest.rds")
  test<-fullTest[,-c(ncol(data))]

  #normalize data
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)
  val<-normalizer(res$validate,means,sds,maxTime)
  train<-normalizer(train,means,sds,maxTime)

  #prepare data for linear model
  linModelTrain<-as.data.frame(rbind(train,val))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )
  times<-head(times, -1)
  times<-tail(times, -1)

@@

#######################
###plot IPA results
#######################

@@

```{r auc}
#######################
###plot AUC results
#######################
AUClist<-readRDS('results/100flchainAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
  aucSims<-cbind(aucSims,sim$AUC)

@@

#######################
###plot C-index results
#######################

### 2023-12-17 analyses/optimMyeloma.Rmd
Improved documentation for potential users

##########################
###Shared Hyperparameters
##########################

min_delta = 0

epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)

reoptimize=FALSE

finalFit=T
```

#5 fold cross validation to select best hyperparameters, average performance on a test set.

@@

library(survival)

data("cancer", package="survival")

preData<-data.frame(year=as.numeric(myeloma$year),
                    entry=as.numeric(myeloma$entry),
                    time=as.numeric(myeloma$futime),
                    status=as.numeric(myeloma$death)
)

@@

saveRDS(res$test,"cvData/myelomaTest.rds")

k=3
klist<-list()
data<-res$train
for(i in 1:k){

  spec = c(train = .85, val = .15)

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/myelomaCV.rds")

@@

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
source_python('src/dsurv.py')
klist<-readRDS("cvData/myelomaCV.rds")
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/myelomaCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/myelomaCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r winners,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/myelomaWins.rds")

@@

```{r bestFits,finalFit}

winners<-readRDS("cvData/myelomaWins.rds")

@@

@@

cidxList<-readRDS('results/100myelomacidx.rds')

temp<-melt(setDT(as.data.frame(cidxList[[1]])), id.vars = c("times"), variable.name = "model")
cidxSims=data.frame(model=temp$model,times=temp$times)

count=1
for(sim in cidxList){
  cidxSims<-cbind(cidxSims, melt(setDT(as.data.frame(sim)), id.vars = c("times"), variable.name = "model")$value)

>>>>

##########################
###Shared Hyperparameters
##########################
min_delta = 0
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
reoptimize=T
finalFit=T
```

# 3 fold cross validation to select best hyperparameters, average performance on a test set.

@@

##############################
### Process data to prepare for analysis
##############################

library(survival)
data("cancer", package="survival")
preData<-data.frame(year=as.numeric(myeloma$year),
                    entry=as.numeric(myeloma$entry),
                    time=as.numeric(myeloma$futime),
                    status=as.numeric(myeloma$death)
)

@@

res = split(data, g)
saveRDS(res$test,"cvData/myelomaTest.rds")

k=3
klist<-list()
data<-res$train
for(i in 1:k){
  spec = c(train = .85, val = .15)
  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/myelomaCV.rds")

@@

##################################
###Set up hyperparameter search space
##################################

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepSurv
###############################
source_python('src/dsurv.py')
klist<-readRDS("cvData/myelomaCV.rds")
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepHit
###############################
klist<-readRDS("cvData/myelomaCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for CBNN
###############################
klist<-readRDS("cvData/myelomaCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r winners,eval=TRUE,hide=FALSE}
###############################
### save the best performaning hyperparameter sets
###############################
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/myelomaWins.rds")

@@

```{r bestFits,finalFit}
#####################################
### run 100 fold bootstrap on the training set for each method
#####################################
winners<-readRDS("cvData/myelomaWins.rds")

@@

#######################
###plot AUC results
#######################

@@

#######################
###plot C-index results
#######################
cidxList<-readRDS('results/100myelomacidx.rds')
temp<-melt(setDT(as.data.frame(cidxList[[1]])), id.vars = c("times"), variable.name = "model")
cidxSims=data.frame(model=temp$model,times=temp$times)
count=1
for(sim in cidxList){
  cidxSims<-cbind(cidxSims, melt(setDT(as.data.frame(sim)), id.vars = c("times"), variable.name = "model")$value)

### 2023-12-17 analyses/optimProstate.Rmd
Improved documentation for potential users

```{r prostatePrep,eval=TRUE,hide=FALSE}

@@

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}

klist<-readRDS("cvData/prostateCV.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/prostateCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/prostateCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

@@

winners<-readRDS("cvData/prostateWins.rds")

@@

AUClist<-readRDS('results/100prostateAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100prostatecidx.rds')

>>>>

```{r prostatePrep,eval=TRUE,hide=FALSE}
##############################
### Process data to prepare for analysis
##############################

@@

##################################
###Set up hyperparameter search space
##################################
lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepSurv
###############################
klist<-readRDS("cvData/prostateCV.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepHit
###############################
klist<-readRDS("cvData/prostateCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for CBNN
###############################
klist<-readRDS("cvData/prostateCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

###############################
### save the best performaning hyperparameter sets
###############################
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

@@

#####################################
### run 100 fold bootstrap on the training set for each method
#####################################
winners<-readRDS("cvData/prostateWins.rds")

@@

#######################
###plot AUC results
#######################
AUClist<-readRDS('results/100prostateAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

#######################
###plot C-index results
#######################
cidxList<-readRDS('results/100prostatecidx.rds')

### 2023-12-17 analyses/optimizeComplex.Rmd
Improved documentation for potential users

##########################
###Shared Hyperparameters
##########################

min_delta = 0

epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)

numSamp<-5000

#baselineTrials<-2

reoptimize=T

finalFit=T
```

#5 fold cross validation to select best hyperparameters, average performance on a test set.

@@

```{r setFixedHyperparameters,eval=TRUE,hide=FALSE}

lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/ComplexSimCV.rds")
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)
```

```{r optimDeepHit,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/ComplexSimCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)
```

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/ComplexSimCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)
```

```{r,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/complexOptimWins.rds")
```

```{r bestFits,eval=T}

winners<-readRDS("cvData/complexOptimWins.rds")

klist<-readRDS("cvData/ComplexSimCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

start_time <- Sys.time()
BrierIPAList<-list()
AUClist<-list()
cScore<-list()
pos<-1

spec = c(train = .85, validate = .15)

@@

  trainOG<-res$train

  numSamp<-nrow(trainOG)
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]

  val<-res$validate

  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)

  fullTest<-readRDS("cvData/ComplexSimTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

  val<-normalizer(res$validate,means,sds,maxTime)

  train<-normalizer(train,means,sds,maxTime)
  linModelTrain<-as.data.frame(rbind(train,val))
 times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

BrierIPAList<-readRDS('results/100complexBrier.rds')

@@

```{r auc}

AUClist<-readRDS('results/100complexAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
   aucSims<-cbind(aucSims,sim$AUC)

@@

cidxList<-readRDS('results/100complexcidx.rds')

temp<-melt(setDT(as.data.frame(cidxList[[1]])), id.vars = c("times"), variable.name = "model")
cidxSims=data.frame(model=temp$model,times=temp$times)

@@

```{r optimDSM,eval=F}
klist<-readRDS("cvData/ComplexSimCV.rds")
test<-readRDS("cvData/ComplexSimTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

>>>>

##########################
###Shared Hyperparameters
##########################
min_delta = 0 
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
numSamp<-5000
reoptimize=T
finalFit=T
```

# 3 fold cross validation to select best hyperparameters, average performance on a test set.

@@

```{r setFixedHyperparameters,eval=TRUE,hide=FALSE}
##################################
###Set up hyperparameter search space
##################################
lr=c(0.001,0.01)
drpt=c(0.01,0.05,0.1)
layer1=c(50,75,100)
layer2=c(10,25,50)
nBatch=c(100,500)
actv=c("relu","linear")#
alp=c(0,0.5,1)

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepSurv
###############################
klist<-readRDS("cvData/ComplexSimCV.rds")
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)
```

```{r optimDeepHit,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for DeepHit
###############################
klist<-readRDS("cvData/ComplexSimCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)
```

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
###############################
### optimize hyperparameters for CBNN
###############################
klist<-readRDS("cvData/ComplexSimCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)
```

```{r,eval=TRUE,hide=FALSE}

###############################
### save the best performaning hyperparameter sets
###############################
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/complexOptimWins.rds")
```

```{r bestFits,eval=T}
#####################################
### run 100 fold bootstrap on the training set for each method
#####################################
#prepare data
winners<-readRDS("cvData/complexOptimWins.rds")
klist<-readRDS("cvData/ComplexSimCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

#initialize data
start_time <- Sys.time()
BrierIPAList<-list()
AUClist<-list()
cScore<-list()
pos<-1

# split training validation sets
spec = c(train = .85, validate = .15)

@@

  #prepare data
  trainOG<-res$train
  numSamp<-nrow(trainOG)
  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  val<-res$validate
  sds<-sapply(train, function(x) (sd(x)))
  means<-sapply(train, function(x) (mean(x)))
  maxTime<-max(train$time)
  fullTest<-readRDS("cvData/ComplexSimTest.rds")
  test<-fullTest[,-c(ncol(data))]
  #normalize data
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)
  val<-normalizer(res$validate,means,sds,maxTime)
  train<-normalizer(train,means,sds,maxTime)
  #prepare data for linear model
  linModelTrain<-as.data.frame(rbind(train,val))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

#######################
###plot IPA results
#######################
BrierIPAList<-readRDS('results/100complexBrier.rds')

@@

```{r auc}
#######################
###plot AUC results
#######################
AUClist<-readRDS('results/100complexAuc.rds')
aucSims=data.frame(model=AUClist[[1]]$model,times=AUClist[[1]]$times)
for(sim in AUClist){
  aucSims<-cbind(aucSims,sim$AUC)

@@

#######################
###plot C-index results
#######################
cidxList<-readRDS('results/100complexcidx.rds')
temp<-melt(setDT(as.data.frame(cidxList[[1]])), id.vars = c("times"), variable.name = "model")
cidxSims=data.frame(model=temp$model,times=temp$times)

@@

```{r optimDSM,eval=F}

################################
### This is kept for transparency
### As DSM did not converge with
### Our hyperparameters and simulation setting 
################################
klist<-readRDS("cvData/ComplexSimCV.rds")
test<-readRDS("cvData/ComplexSimTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)
